Something with Objects and Names

### 2019-12-05 papers/ACL2020/experiments.tex

>>>>

\begin{table*}[t]
\centering
	\small
\begin{tabular}{lrrr||rrr}
\toprule
&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
\midrule
       FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
        FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
        		\midrule \midrule
 FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
 		\midrule 
     ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
     ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
    ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
\bottomrule

\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:errors_agreement}}
\end{table*}
